Psychological Needs During Intergroup Contact

### 2021-10-04 PreregistrationAOT-M.Rmd
first draft

---
title           : "Preregistration of Psychological Needs During Intergroup Contact --- Sample: Young Medical Professionals"
shorttitle      : "Preregistration AOT-M"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: references.bib
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

@@

1. Contact Hypothesis
    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
    a. T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$
    a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
1. Allport's Conditions
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + u_{oj} + r_{ij}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$

@@

Enter your response here.

@@

Enter your response here.

@@

Enter your response here.

@@

Enter your response here.

>>>>

---
title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: references.bib
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

@@

1. Contact Hypothesis
    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
    a. T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
    a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
1. Allport's Conditions
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + u_{oj} + r_{ij}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$

@@

We will use the standard p<.05 criteria for determining whether the correlation and regression coefficients are statistically significant. However, given the large sample size we will place a particular emphasis on effect sizes in our interpretations of the results.

@@

No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the variables of interest for a given analysis. Outliers will be included in the analysis.

@@

Given the (unexpectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.

@@

@Brown2005 proposed in their integrative theory of intergroup contact that "group salience" should moderate the positive effect of intergroup contact on outgroup attitudes. They argue that especially when the outgroup membership is salient, the positive attitudes should generalize from the outgroup individual to the general outgroup. We have data to test this hypothesis within a large intensive longitudinal dataset of daily intergroup interactions. We do this by seperately assessing attitudes towards the outgroup interaction partner and the outgroup generally. And by assessing whether perceiving the interaction as representative of the outgroup moderates the positive contact effects.

To build confidence in our conclusions about the role of contact quality we calculate an alternative measure of interaction quality that includes perceived pleasantness, meaning, effectiveness, and importance of the interaction.

We expect that certain contextual characteristics may be related to the positive effects of high quality outgroup interactions. Therefore, we will look for the effect of key need fulfillment on outgroup attitudes while also including information about the interaction partner (perceived closeness, trust, relationship), the interaction characteristics (duration, interaction language, group vs. dyadic), as well as characteristics of the key need (importance of the need, fulfillment due to the interaction partner).
